---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# immosaic

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of immosaic is to create packed image mosaic. The main function `immosaic`, takes a set of images, or a function that generates images and packs them into a larger image as tightly as possible, scaling as necessary, using a greedy algorithm (so don't expect it to be fast!). It is largely based on []

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rdinnager/immosaic")
```
## Example

```{r load_package}
library(immosaic)
library(Rvcg)
library(rgl)
```

```{r gen_shapes}

generate_platonic <- function(i, width = 200, height = 200, cols = rainbow(100)) {
  
  shape <- sample(c("sphere",
                    "spherical_cap",
                    "tetrahedron",
                    "dodecahedron",
                    "octahedron",
                    "icosahedron",
                    "hexahedron",
                    "cube",
                    "cone"),
                  1)
  
  mesh <- switch (shape,
    sphere = Rvcg::vcgSphere(),
    spherical_cap = Rvcg::vcgSphericalCap(),
    tetrahedron = Rvcg::vcgTetrahedron(),
    dodecahedron = Rvcg::vcgDodecahedron(),
    octahedron = Rvcg::vcgOctahedron(),
    icosahedron = Rvcg::vcgIcosahedron(),
    hexahedron = Rvcg::vcgHexahedron(),
    cube = Rvcg::vcgBox(),
    cone = Rvcg::vcgCone(2, 0, 6)
  )
  
  scales <- c(1, 1, 1, 1, 1, 1, 1, 1, 2, 2, 3, 4)
  mesh <- rgl::scale3d(mesh, 
                       sample(scales, 1),
                       sample(scales, 1),
                       sample(scales, 1))
  
  mesh <- rgl::rotate3d(mesh, runif(1, 0, 2 * pi), 0, 0, 1)
  mesh <- rgl::rotate3d(mesh, runif(1, 0, 2 * pi), 0, 1, 0)
  mesh <- rgl::rotate3d(mesh, runif(1, 0, 2 * pi), 1, 0, 0)
  
  rgl::shade3d(mesh, col = sample(cols, 1),
               specular = "grey")
  
  png_file <- tempfile(fileext = ".png")
  rgl::snapshot3d(filename = png_file, width = width, height = height,
                  webshot = FALSE)
  rgl::close3d()
  
  im2 <- imager::load.image(png_file)
  im <- imager::imfill(width, height, val = c(0, 0, 0, 1))
  im[ , , , 1:3] <- im2 
  im[imager::R(im) == 1 & imager::G(im) == 1 & imager::B(im) == 1] <- 0
  
  im  
 
}

```
